---
title: "Canadian Turbines"
output: html_notebook
---
## Canadian Turbines

```{r}
# loading the data

wind_turbine <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-10-27/wind-turbine.csv')

```
### First, we'll find out how many GW of clean energy, coming from eolic turbines, does Canada owns on every Province·

```{r}

wind_turbine %>% 
  mutate(turbine_rated_capacity_m_w = turbine_rated_capacity_k_w / 1000) %>% 
  count(province_territory, wt = turbine_rated_capacity_m_w, sort = TRUE) %>% 
  mutate(province_territory = fct_reorder(province_territory, n)) %>% 
  ggplot(aes(province_territory, n, fill = province_territory))+
  geom_col() +
  coord_flip() +
  labs(title = "Canadian GW availability per Province", 
       x = "Province",
       y = "Total MW Capacity") +
  theme(legend.position = "none")
  
```
Is the turbine generated electricity directed to residential usage?
Is Ontario or Quebec the more populated provinces in Canada?
Does this data goes in accordance to that?


### Secondly: How was the unfolding of the Canadian capacity commissioning 

```{r}
wind_turbine %>% 
  count(commissioning_date, wt=turbine_rated_capacity_k_w / 1000) %>% 
  ggplot(aes(commissioning_date, n, fill = commissioning_date)) +
  geom_col() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  theme(legend.position = "none") +
  labs(title = "Turbine commissioning unfolding", 
       x = "Year",
       y = "Total MW Capacity") +
  theme(legend.position = "none")
```

Have they've reached needed capacity circa 2014/2015?
After that period it appears to be a decline in commissioning. 
ToDo: cross this data with population, density, electrical capacity in order to test for the previous question.





